%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\cvsubsection{Article in peer-reviewed journals}

%------------------------------------------------
% Usage: \cvarticle{<author>}{<title>}{<journal>}{<page>}

\cvarticle
{A. Downs, Z. Kootbally, W. Harrison, P. Pilliptchak, B. Antonishek, M. Aksu, C. Schlenoff, and S.K. Gupta:} % Author
{1}{Assessing Industrial Robot Agility through International Competitions} % Title
{Robotics and Computer-Integrated Manufacturing} % Journal
{2021} % Year
{71} % Volume
{x} % Number
{102113} % Pages
{Oct} % Month


\cvarticle
{Z. Kootbally, C. Schlenoff, B. Antonishek, F. Proctor, T. Kramer, W. Harrison, A. Downs, and S. Gupta} % Author
{2}{Enabling Robot Agility in Manufacturing Kitting Applications} % Title
{Integrated Computer-Aided Engineering (ICAE)} % Journal
{2018} % Year
{25} % Volume
{2} % Number
{193--212} % Pages
{xx} % Month

\cvarticle
{Z. Kootbally, T.R. Kramer, C. Schlenoff, and S.K. Gupta} % Author
{3}{Implementation of an Ontology-based Approach to Enable Agility in Kit Building Applications} % Title
{International Journal of Semantic Computing} % Journal
{2018} % Year
{12} % Volume
{1} % Number
{5--24} % Pages
{March} % Month

\cvarticle
{Z. Kootbally} % Author
{4}{Industrial Robot Capability Models for Agile Manufacturing} % Title
{Industrial Robot: An International Journal} % Journal
{2016} % Year
{Vol. 43} % Volume
{Iss. 55} % Number
{pp. 481--494} % Pages
{} % Month

\cvarticle
{F.M. Proctor, S.B. Balakirsky, Z. Kootbally, T.R. Kramer, C.I. Schlenoff, and W.P. Shackelford} % Author
{5}
{The Canonical Robot Command Language (CRCL)} % Title
{Industrial Robot: An International Journal} % Journal
{2016} % Year
{Vol. 43} % Volume
{Iss. 55} % Number
{pp. 495--502} % Pages
{} % Month



\cvarticle
{Z. Kootbally, C. Schlenoff, C. Lawler, T. Kramer, and S.K. Gupta} % Author
{6}
{Towards Robust Assembly with Knowledge Representation for the Planning Domain Definition Language (PDDL)} % Title
{Robotics and Computer-Integrated Manufacturing} % Journal
{2015} % Year
{33} % Volume
{} % Number
{pp. 42--55} % Pages
{(Jun)} % Month

%------------------------------------------------
\cvarticle
{C. Schlenoff, Z. Kootbally, A. Pietromartire, M. Franaszek, and S. Foufou} % Author
{7}{Intention Recognition in Manufacturing Applications} % Title
{Robotics and Computer-Integrated Manufacturing} % Journal
{2015} % Year
{33} % Volume
{} % Number
{pp. 29--41} % Pages
{(Jun)} % Month

%------------------------------------------------
\cvarticle
{S. Balakirsky, Z. Kootbally, T. Kramer, A. Pietromartire, C. Schlenoff, and S.K. Gupta} % Author
{8}{Knowledge Driven Robotics for Kitting Applications} % Title
{Robotics and Autonomous Systems} % Journal
{2013} % Year
{61} % Volume
{(11)} % Number
{pp. 1205--1214} % Pages
{(Sep)} % Month


%------------------------------------------------
\cvarticle
{C. Schlenoff, A. Pietromartire, Z. Kootbally, S. Balakirsky, and S. Foufou} % Author
{9}{Ontology-based State Representations for Intention Recognition in Human–robot Collaborative Environments} % Title
{Robotics and Autonomous Systems} % Journal
{2013} % Year
{61} % Volume
{(11)} % Number
{pp. 1224--1234} % Pages
{(Sep)} % Month

%------------------------------------------------
\cvarticle
{Z. Kootbally, C. Schlenoff, and R. Madhavan} % Author
{10}{Performance Assessment of PRIDE in Manufacturing Environments} % Title
{ITEA Journal of Test \& Evaluation} % Journal
{2010} % Year
{31} % Volume
{(3)} % Number
{pp. 410--422} % Pages
{(Sep)} % Month

\cvsubsection{\newline Book chapters}


\cvarticle
{C. Schlenoff, Z. Kootbally, W. Shackleford, F. Proctor, B. Antonishek, W. Harrison, and A. Downs} % Author
{1}{Agile Industrial Robots.} % Title
{Manufacturing in the Era of 4th Industrial Revolution} % Journal
{2021} % Year
{Volume 2: Recent Advances in Industrial Robotics} % Volume
{} % Number
{pp. 7--42} % Pages
{} % Month


\cvarticle
{Z. Kootbally, S. Balakirsky, and A. Visser} % Author
{2}{Enabling Codesharing in Rescue Simulation with USARSim/ROS.} % Title
{RoboCup 2013: Robot World Cup XVII. Ed. S. Behnke, M. Veloso, A. Visser, and R. Xiong. Lecture Notes in Computer Science. Springer Berlin Heidelberg} % Journal
{2014} % Year
{Vol. 8371} % Volume
{} % Number
{pp. 592--599} % Pages
{} % Month

\cvarticle
{Z. Kootbally, C. Schlenoff, T. Weisman, S. Balakirsky, T. Kramer, and A. Pietromartire} % Author
{3}{A Simulated Sensor-Based Approach for Kit Building Applications.} % Title
{Robot Intelligence Technology and Applications 2. Ed. by J-H. Kim, E.T. Matson, H. Myung, P. Xu, and F. Karray. Advances in Intelligent Systems and Computing. Springer International Publishing} % Journal
{2014} % Year
{Vol. 271} % Volume
{} % Number
{pp. 241--257} % Pages
{} % Month

\cvarticle
{S. Balakirsky and Z. Kootbally} % Author
{4}{An Ontology Based Approach to Action Verification for Agile Manufacturing.} % Title
{Robot Intelligence Technology and Applications 2. Ed. by J-H. Kim, E.T. Matson, H. Myung, P. Xu, and F. Karray. Advances in Intelligent Systems and Computing. Springer International Publishing} % Journal
{2014} % Year
{Vol. 274} % Volume
{} % Number
{pp. 201--217} % Pages
{} % Month

\cvarticle
{C. Schlenoff, A. Pietromartire, Z. Kootbally, S. Balakirsky, S. Foufou} % Author
{5}{Inferring Intention through State Representations in Cooperative Human-Robot Environments.} % Title
{Engineering Creative Design in Robotics and Mechatronics. Ed. by M.K. Habib and J.P. Davim. Advances in Mechatronics and Mechanical Engineering} % Journal
{2013} % Year
{Chap. 9} % Volume
{} % Number
{pp. 122--151} % Pages
{Jun} % Month

%---------------------------------------------------------------------------------------------------------

\cvsubsection{\newline Full paper refereed research related publications in conferences}

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{A. Downs, Z. Kootbally, and C. Schlenoff}%Author
{1}{Agility Metrics in the ARIAC Competition}%title
{International Conference on Advanced Robotics and Its Social Impacts (ARSO 2020)}%conference
{2020}%year
{pp. 240--245}%pages
{Oct}%month

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{Z. Kootbally, T. Kramer, C. Schlenoff, and S.K. Gupta}%Author
{2}{Overview of an Ontology-based Approach for Kit  Building Applications}%title
{IEEE International Conference on Semantic Computing - Semantic Robotics}%conference
{2017}%year
{pp. 520--525}%pages
{Jan}%month

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{T. Kramer, Z. Kootbally, S. Balakirsky, C. Schlenoff, A. Pietromartire, and S.K. Gupta}%Author
{3}{Performance evaluation of knowledge-based kitting via simulation}%title
{IEEE International Conference on Automation Science and Engineering (CASE)}%conference
{2013}%year
{pp. 356--361}%pages
{Aug}%month

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{S. Balakirsky and Z. Kootbally}%Author
{4}{USARSim/ROS: A Combined Framework for Robotic Control and Simulation}%title
{ASME/ISCIE 2012 International Symposium on Flexible Automation}%conference
{2012}%year
{pp. 101--108}%pages
{Jun}%month

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{S. Balakirsky, Z. Kootbally, C. Schlenoff, T. Kramer, and S.K. Gupta}%Author
{5}{An Industrial Robotic Knowledge Representation for Kit Building Applications}%title
{Proceedings of the 2012 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}%conference
{2012}%year
{pp. 1365--1370}%pages
{Oct}%month



\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{R. Madhavan, Z. Kootbally, and C. Schlenoff}%Author
{6}{Prediction in Dynamic Environments for Autonomous On-Road Driving}%title
{9th International Conference on Control, Automation, Robotics and Vision (ICARCV'06)}%conference
{2006}%year
{pp. 1--6}%pages
{Dec}%month

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{C. Schlenoff, R. Madhavan, and Z. Kootbally}%Author
{7}{PRIDE: A Hierarchical, Integrated Prediction Framework for Autonomous On-road Driving}%title
{Proceedings 2006 IEEE International Conference on Robotics and Automation (ICRA)}%conference
{2006}%year
{pp. 2348--2353}%pages
{May}%month

\cvsubsection{\newline Abstract refereed publications in conferences and workshops}


\cvinproceedings
{A. Ferrando, Z. Kootbally, P. Piliptchak, R.C. Cardoso, C. Schlenoff, and M. Fisher:}%Author
{1}{Runtime Verification of the ARIAC Competition: Can a Robot be Agile and Safe at the same time?}%title
{The 7th Italian Workshop on Artificial Intelligence and Robotics}%conference
{2020}%year
{7--11}%pages
{Nov}%month


\cvinproceedings
{B. Weiss, L. Fronczek, E. Morse, Z. Kootbally, and C. Schlenoff}%Author
{2}{Performance Assessments of Android-powered Military Applications Operating on Tactical Handheld Devices}%title
{Proc. SPIE 8755, Mobile Multimedia/Image Processing, Security, and Applications}%conference
{2013}%year
{}%pages
{Jun}%month

\cvinproceedings
{S. Balakirsky, Z. Kootbally, T. Kramer, R. Madhavan, C. Schlenoff, and M. Shneier}%Author
{3}{Functional Requirements of a Model for Kitting Plans}%title
{Proceedings of the Workshop on Performance Metrics for Intelligent Systems}%conference
{2012}%year
{pp. 29--36}%pages
{Mar}%month

\cvinproceedings
{C. Schlenoff, A. Pietromartire, Z. Kootbally, S. Balakirsky, and S. Foufou}%Author
{4}{Ontology-based State Representation for Intention Recognition in Cooperative Human-robot Environments}%title
{Proceedings of the 2012 ACM Conference on Ubiquitous Computing. UbiComp’12}%conference
{2012}%year
{pp. 810--817}%pages
{Sep}%month

\cvinproceedings
{Z. Kootbally, C. Schlenoff, and R. Madhavan}%Author
{5}{Fuzzy-logic-based Approach for Identifying Objects of Interest in the PRIDE Framework}%title
{Proceedings of the 8th Workshop on Performance Metrics for Intelligent Systems}%conference
{2008}%year
{pp. 17--24}%pages
{Aug}%month

\cvinproceedings
{Z. Kootbally, C. Schlenoff, R. Madhavan, and S. Foufou}%Author
{6}{Performance Evaluation of Cost-based vs. Fuzzy-logic-based Prediction Approaches in PRIDE}%title
{SPIE Defense and Security Symposium}%conference
{2008}%year
{}%pages
{Apr}%month



\cvinproceedings
{Z. Kootbally, C. Schlenoff, and R. Madhavan}%Author
{7}{A Brief History of PRIDE}%title
{Proceedings of the 2007 Workshop on Performance Metrics for Intelligent Systems}%conference
{2007}%year
{pp. 40--47}%pages
{Aug}%month

\cvinproceedings
{C. Schlenoff, Z. Kootbally, and R. Madhavan}%Author
{8}{Driver Aggressivity Analysis within the Prediction in Dynamic Environments (PRIDE) Framework}%title
{Proceedings of the 2007 SPIE Defense and Security Symposium}%conference
{2007}%year
{}%pages
{May}%month

\cvinproceedings
%{<author>}{<title>}{<booktitle>}{<year>} {<pages>} {<month>}
{Z. Kootbally, C. Schlenoff, and R. Madhavan}%Author
{9}{Prediction in Dynamic Environments via Identification of Critical Time Points}%title
{Military Communications Conference (MILCOM 2006)}%conference
{2006}%year
{pp. 1--7}%pages
{Oct}%month

\cvsubsection{\newline Technical reports}

\cvtechreport
{T.R. Kramer, B.J. Marks, C. Schlenoff, S. Balakirsky, Z. Kootbally, and A. Pietromartire}% {author}
{1}{Software Tools for XML to OWL Translation}%title
{National Institute of Standards and Technology}%institution
{2015}%year
{Internal}%type
{NISTIR 8068}%number
{Gaithersburg, MD, USA}%address
{Jun}%month

\cvtechreport
{S. Balakirsky, T. Kramer, Z. Kootbally, and A. Pietromartire}% {author}
{2}{Metrics and Test Methods for Industrial Kit Building}%title
{National Institute of Standards and Technology}%institution
{2013}%year
{Internal}%type
{NISTIR 7942}%number
{Gaithersburg, MD, USA}%address
{May}%month

\cvsubsection{\newline Theses}

\cvphdthesis
{Z. Kootbally}
{Moving Object Predictions in Dynamic Environments for Autonomous Ground Vehicles}
{University of Burgundy}
{Dijon, France}
{2010}
{Dec}


